\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}

\geometry{
top=0.5in,
bottom=1in,
left=1in,
right=1in
}

\title{\textbf{Problem Set Four}}
\author{Devin Williams}
\date{\today}

\begin{document}

\maketitle

\begin{itemize}
     \item Issues with running script in R, Java continually is defaulting to a older version. Seems to be running now, and will run outside of OSCER. Tried to implement change mentioned in email but have not been able to fix it fully. 
    \item Data Sources
        \begin{itemize}
            \item[$\diamond$] I am very interested in looking at data scraping for multiple different sources. Including...
                \begin{itemize}
                    \item[$\diamond$] Professional soccer player values in leagues around the world. 
                \end{itemize}
                \begin{itemize}
                    \item[$\diamond$] Transit data including things like rider patterns or bus schedules.
                \end{itemize}
                 \begin{itemize}
                    \item[$\diamond$] NFL performance statistics year over year. 
                \end{itemize}
                \begin{itemize}
                    \item[$\diamond$] Professional athletes interview scripts. 
                \end{itemize}
                \begin{itemize}
                    \item[$\diamond$] Boeing flight data, looking at how true issues with their planes are. 
                \end{itemize}
        \end{itemize}
    \item Question One: Check what type of object mydf is. What type of an object is mydf\$date?
       \begin{itemize}
            \item[$\diamond$] It is a character. 
        \end{itemize}
    \item Question Two: Verify that the two dataframe are different types: type class(df1) and class(df). What is the class of each?
        \begin{itemize}
            \item[$\diamond$] There are two different classes: df1 is tbl\_df and df2 is tbl\_spark
        \end{itemize}
    \item Question Three: Are the column names any different across the two objects? If so, why might that be?
        \begin{itemize}
             \item[$\diamond$] For the dataframe labeled "df" has the column names: Sepal\_Length, Sepal\_Width, Petal\_Length, Petal\_Width, Species. While the dataframe labeled "df1" has the column names: Sepal.Length, Sepal.Width, Petal.Length, Petal.Width, Species
        \end{itemize}
        \begin{itemize}
             \item[$\diamond$] Spark typically uses an underscore as a separator rather than a dot like R. This is why df1 has dots and df has underscores in this example. 
        \end{itemize}
        \end{itemize}
\end{document}
