\documentclass[12pt,letterpaper]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{tabularray}
\usepackage{siunitx}     
\usepackage{booktabs}
\usepackage{float}

\geometry{
  top=1in,
  bottom=1in,
  left=1in,
  right=1in
}

\title{\textbf{Problem Set Nine}}

\author{Devin Williams}
\date{\today}

\begin{document}

\maketitle

\section{Dimension of Training Data and amount of X Variables: Q7}
\begin{itemize}
  \item What is the dimension of your training data (housing\_train)? 
    \begin{itemize}
        \item The dimensions of the training data were 404 to 14.
    \end{itemize}
  \item How many more X variables do you have than in the original housing data?
    \begin{itemize}
        \item  There are 61 more x variables than the original housing data.
    \end{itemize}
\end{itemize}

\section{Lasso: Q8}
\begin{itemize}
  \item What is the optimal value of Lambda? 
    \begin{itemize}
        \item The optimal Lambda value is 0.00139 based on the code. 
    \end{itemize}
    \item What is the in-sample RMSE? 
    \begin{itemize}
        \item The in-sample RMSE was estimated from the cross-validation results, which is 0.0632 as shown in the "mean" column. This is the average RMSE across the 6-fold cross-validation on the training data.
    \end{itemize}
     \item What is the out-of-sample RMSE (i.e. the RMSE in the test data)? 
    \begin{itemize}
        \item It shows an RMSE of 0.170 for "Preprocessor1\_Model1". This is the RMSE on your test data (out-of-sample).
    \end{itemize}
\end{itemize}

\section{Ridge: Q9}
\begin{itemize}
  \item What is the optimal value of Lambda now?
    \begin{itemize}
        \item  The ridge regression model is 0.0233, as shown in the "penalty" column of the ridge\_top\_rmse output. 
    \end{itemize}
    \item What is the out-of-sample RMSE? 
    \begin{itemize}
        \item The out-of-sample RMSE for the ridge regression model is 0.173, as shown in the first table.
    \end{itemize}
\end{itemize}

\section{Question 10}
\begin{itemize}
  \item Would you be able to estimate a simple linear regression model on a data set that had more columns than rows?
    \begin{itemize}
        \item You cannot estimate a simple linear regression model on a dataset that has more predictors (columns) than observations (rows). This creates a under determined system where there are infinite solutions that perfectly fit the training data. 
    \end{itemize}
    \item Where the model stands in terms of the bias-variance trade-off.
    \begin{itemize}
        \item Both models show significant gaps between in-sample and out-of-sample performance. This indicates some overfitting. Overall, the LASSO model performs better in both in- and out-of-sample fits. The optimal regularization parameters (Lambda = 0.00139 for LASSO and Lambda = 0.0233 for Ridge) show that Ridge requires stronger regularization than LASSO to achieve its best performance.
    \end{itemize}
\end{itemize}
\end{document}