\documentclass[11pt,letterpaper]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}

\geometry{
top=0.5in,
bottom=1in,
left=1in,
right=1in
}

\title{\textbf{Problem Set Two}}
\author{Devin Williams}
\date{\today}

\begin{document}

\maketitle

\section*{Main Tools of a Data Scientist}

\begin{itemize}
    \item Measurement
        \begin{itemize}
            \item[$\diamond$] How insights and policies are constructed.
        \begin{itemize}
            \item[$\diamond$] You can't construct a policy without measuring what the policy is meant to accomplish in the end. 
        \end{itemize}
        \end{itemize}
    \item Statistical programming languages
       \begin{itemize}
        \item[$\diamond$] R
        \item[$\diamond$] Python
        \item[$\diamond$] Julia
        \item[$\diamond$] Stata
        \item[$\diamond$] SAS
        \item[$\diamond$] SPSS
        \item[$\diamond$] Matlab
        \item[$\diamond$] JavaScript
        \end{itemize}
    \item Visualization tools
        \begin{itemize}
        \item[$\diamond$] Very important tools for data scientists in different coding languages.
            \begin{itemize}
        \item[$\diamond$] ggplot2 (R)
        \item[$\diamond$] matplotlib (Python)
        \item[$\diamond$] Plots.jl (Julia)
        \item[$\diamond$] Tableau
        \item[$\diamond$] Modeling
            \end{itemize}
        \end{itemize}
    \item Big Data management software
        \begin{itemize}
            \item[$\diamond$] There is often data sets that are too being for things like R or Python to handle. There are multiple other programs that can help analyze data if the data set is too large.
                \begin{itemize}
                    \item[$\diamond$] RDDs
                    \item[$\diamond$] SQL
                \end{itemize}
        \end{itemize}
    \item Data collection tools
        \begin{itemize}
            \item[$\diamond$] There is many different ways to collect data as a data scientist. Using these tools makes data analysis easier in many different ways. 
                \begin{itemize}
                    \item[$\diamond$] Web scraping
                \begin{itemize}
                    \item[$\diamond$] Can be done in almost every coding language available for use. 
                \end{itemize}
                \end{itemize}
        \end{itemize}
        \end{itemize}
\end{document}
